Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-19 paper/paper.tex
Add results

@@

\begin{table*}[ht]
  \centering
  \begin{tabularx}{\textwidth}{lXllll}
    \toprule
    System & Features & Tasks & Subtask A & Subtask B & Multi-span \\
    \midrule
    Codestrange & 				 \\
    GuanZhengyi & BETO & Only A & Sequence & - & BIO \\
    IXA & ROBERTa & Sequential & Sequence & Sequence & BIO \\
    JAD & BERT & Joint & Token & Pairwise & Relation \\
    Maoqin & BERT & Only A & Sequence & - & BIO \\
    PUCRJ-PUCPR-UFMG & BERT & Joint & Sequence & Pairwise & BIO \\
    uhKD4 & Word2vec POS-tag Character Position & Sequential & Sequence & Pairwise & BILOUV \\
    UH-MMM & BERT FastText POS-tag Dependency Character & Sequential & Sequence & Pairwise & BILOUV \\
    Vicomtech Joint & BERT & Joint & Sequence & Pairwise & BIO \\
    Vicomtech Seq2Seq & T5 & Joint & Text2text & Text2text & Text \\
    \bottomrule
  \end{tabularx}
  \caption{Summary of the approaches presented at the eHealth-KD Challenge.\label{tab:participants}}
\end{table*}

@@

\begin{table}
  \caption{Results.\label{tab:results}}
\end{table}

>>>>

\begin{table*}[t!]
  \centering
  \begin{tabularx}{\textwidth}{lXllll}
    \toprule
    System & Features & Tasks & Subtask A & Subtask B & Multi-span \\
    \midrule
    Codestrange & 				 \\
    GuanZhengyi & BETO & Only A & Sequence & - & BIO \\
    IXA & ROBERTa & Sequential & Sequence & Sequence & BIO \\
    JAD & BERT & Joint & Token & Pairwise & Relation \\
    Maoqin & BERT & Only A & Sequence & - & BIO \\
    PUCRJ-PUCPR-UFMG & BERT & Joint & Sequence & Pairwise & BIO \\
    uhKD4 & Word2vec POS-tag Character Position & Sequential & Sequence & Pairwise & BILOUV \\
    UH-MMM & BERT FastText POS-tag Dependency Character & Sequential & Sequence & Pairwise & BILOUV \\
    Vicomtech Joint & BERT & Joint & Sequence & Pairwise & BIO \\
    Vicomtech Seq2Seq & T5 & Joint & Text2text & Text2text & Text \\
    \bottomrule
  \end{tabularx}
  \caption{Summary of the approaches presented at the eHealth-KD Challenge.\label{tab:participants}}
\end{table*}

@@

@@

\begin{table*}
  \resizebox{\textwidth}{!}{
  \begin{tabular}{lccccccccc}
    \toprule
    & \multicolumn{3}{c}{\textbf{Main}} & \multicolumn{3}{c}{\textbf{Task A}} & \multicolumn{3}{c}{\textbf{Task B}} \\
    \textbf{Team}    & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$   & $F_1$ & $P$   & $R$ \\
    \midrule
    Vicomtech        & 0.531 & 0.540 & 0.534 & 0.684 & 0.699 & 0.747 & 0.371 & 0.541 & 0.283 \\
    PUCRJ-PUCPR-UFMG & 0.528 & 0.568 & 0.502 & 0.706 & 0.714 & 0.697 & 0.263 & 0.366 & 0.205 \\
    IXA              & 0.498 & 0.464 & 0.538 & 0.653 & 0.613 & 0.698 & 0.430 & 0.453 & 0.409 \\
    uhKD4            & 0.422 & 0.485 & 0.374 & 0.527 & 0.517 & 0.537 & 0.317 & 0.556 & 0.222 \\
    UH-MMM           & 0.338 & 0.291 & 0.403 & 0.607 & 0.546 & 0.685 & 0.053 & 0.077 & 0.041 \\
    Codestrange      & 0.232 & 0.337 & 0.176 & 0.080 & 0.415 & 0.044 & 0.032 & 0.437 & 0.017 \\
    baseline         & 0.232 & 0.337 & 0.176 & 0.306 & 0.350 & 0.271 & 0.032 & 0.437 & 0.017 \\
    JAD              & 0.109 & 0.234 & 0.071 & 0.262 & 0.315 & 0.224 & 0.007 & 0.375 & 0.003 \\
    GuanZhengyi      & -     & -     & -     & 0.334 & 0.520 & 0.245 & -     & -     & -     \\
    Maoqin           & -     & -     & -     & 0.173 & 0.271 & 0.127 & -     & -     & -     \\
    \bottomrule
  \end{tabular}}

  \caption{Results.\label{tab:results}}
\end{table*}
